Deep Learning

### 2015-02-01 deepreview.tex
modified the fprop/bprop box captions as suggested by Geoff to include the 3 non-linearities

\begin{figure}[htp]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\fbox{\includegraphics[width=0.69\linewidth]{netvis-simple-2S.png}}
\fbox{\includegraphics[width=0.28\linewidth]{chain-rule.pdf}}}
\centerline{
\hspace*{.5mm}\fbox{\includegraphics[width=0.49\linewidth]{bpfig_forward.pdf}}
\hspace*{0mm}\fbox{\includegraphics[width=0.49\linewidth]{bpfig_backward.pdf}}
}
\caption{
{\bf Top left.} A multi-layer neural network can distort the
input space to make the classes (whose examples are supposed to
be on the red and blue lines, here) linearly separable. Note how
a regular grid in input space is also transformed. This is an
illustrative example with only two input units, two hidden units
and one output unit, but the networks used for object recognition
or natural language processing contain tens or hundreds of thousand
of units. Reproduced with permission by Chris Olah from~\url{http://colah.github.io/}.
\newline
{\bf Top right.} The chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly,
the change $\Delta y$ creates a change $\Delta z$ in $z$. Substituting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). \newline
{\bf Bottom left.} The equations used for computing the forward pass in a neural net
with two hidden layers (each composed of a group of hidden units that are
similarly connected). At each layer, we first compute the total input,
$z$, to each unit which is a weighted sum of the outputs of the units in
the layer below. Then a non-linear function $f(.)$ is applied to $z$ to get
the output of the unit.  For simplicity, we have omitted bias terms. \newline
{\bf Bottom right.} The equations used for computing the backward pass. At each hidden
layer we compute the error-derivative w.r.t. the output of each unit which
is a weighted sum of the error-derivatives w.r.t. the total inputs to the
units in the layer above. We then convert the error-derivative w.r.t. the
output into the error-derivative w.r.t. the input by multipling it by the
derivative of $f(z)$.  At the output layer, the error-derivative w.r.t. the
output of a unit is computed by differentiating the cost function. This
gives $y_l-t_l$ If the cost function for unit $l$ is $0.5(y_l-t_l)^2$ where
$t_l$ is the target value.
}
\label{fig:backprop-box}
\end{minipage}
}
\end{figure}

>>>>

\begin{figure}[htp]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\fbox{\includegraphics[width=0.69\linewidth]{netvis-simple-2S.png}}
\fbox{\includegraphics[width=0.28\linewidth]{chain-rule.pdf}}}
\centerline{
\hspace*{.5mm}\fbox{\includegraphics[width=0.49\linewidth]{bpfig_forward.pdf}}
\hspace*{0mm}\fbox{\includegraphics[width=0.49\linewidth]{bpfig_backward.pdf}}
}
\caption{
{\bf Top left.} A multi-layer neural network can distort the
input space to make the classes (whose examples are supposed to
be on the red and blue lines, here) linearly separable. Note how
a regular grid in input space is also transformed. This is an
illustrative example with only two input units, two hidden units
and one output unit, but the networks used for object recognition
or natural language processing contain tens or hundreds of thousand
of units. Reproduced with permission by Chris Olah from~\url{http://colah.github.io/}.
\newline
{\bf Top right.} The chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly,
the change $\Delta y$ creates a change $\Delta z$ in $z$. Substituting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). 
\newline
{\bf Bottom left.} 
The equations used for computing the forward pass in a neural
net with two hidden layers. At each layer, we first compute the total
input $z$ to each unit, which is a weighted sum of the outputs of the
units in the layer below. Then a non-linear function $f(.)$ is applied
to $z$ to get the output of the unit.  For simplicity, we have omitted
bias terms. The functions commonly used in neural networks include the
logistic sigmoid, $f(z) = 1/(1+\exp(-z))$, the hyberbolic tangent,
$f(z) = (\exp(z)-\exp(-z))/(\exp(z)+\exp(-z))$ and, more recently, the
rectified linear unit, $f(z) = max(0, z)$.
{\bf Bottom right.} 
The equations used for computing the backward pass. At each
hidden layer we compute the error-derivative w.r.t. the output of each
unit which is a weighted sum of the error-derivatives w.r.t. the total
inputs to the units in the layer above. We then convert the
error-derivative w.r.t. the output into the error-derivative w.r.t.
the input by multipling it by the gradient of $f(z)$.  At the output
layer, the error-derivative w.r.t. the output of a unit is computed by
differentiating the cost function. This gives $y_l-t_l$ if the cost
function for unit $l$ is $0.5(y_l-t_l)^2$ where $t_l$ is the target
value. Once the $\partial E/\partial z_k$ is known, the
error-derivative for the weight $w_{jk}$ on the connection from unit
$j$ in the layer below is just $y_j \partial E/\partial z_k$.
}
\label{fig:backprop-box}
\end{minipage}
}
\end{figure}
